---
title: "Class 11"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections:true
    code_download: true
    code_folding: true
date: "2026-09-30"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Learning objectives
 Scape multiple wepages from the same site using a for loop approach
 Enable me to scrape multiple webpages rom teh same site using the [purr] package which is a functional programming approach (we create our own function in this process)
 
## Re-examine the bulletin example

Try to expand on the example form last class to include the following:

[ACC](https://bulletin.miamioh.edu/courses-instruction/acc/),
[BUS](https://bulletin.miamioh.edu/courses-instruction/bus/),
[ISA](https://bulletin.miamioh.edu/courses-instruction/isa/), and
[MKT](https://bulletin.miamioh.edu/courses-instruction/mkt/).

You can repeat your code a few times changing the URL, but it would normally be tedious. We will follow the DRY principle which means Don't Repeat Yourself

```{r bulletin}
dept_abbrv = c('acc', 'bus', 'isa', 'mkt')
courses_df = data.frame() # Initializing conytainedto store stuff from the loop
for (abbrv in dept_abbrv) {
  cat(rep("-", 50), "\n")
  print(abbrv)
  bulletin_url = paste0('https://bulletin.miamioh.edu/courses-instruction/', abbrv, '/')
# Made the webpage an R object because we're gonna be using it several times while only changng the URL
webpage = rvest::read_html(bulletin_url)

webpage |> rvest::html_elements("p.courseblocktitle") |> rvest::html_text2() -> titles
webpage |> rvest::html_elements("p.courseblockdesc") |> rvest::html_text2() -> descs

df = data.frame(title = titles, desc = descs)
print(df$title[1:2])
courses_df = rbind(courses_df,df)
}

```

## purrr approach for same problem

This is a functional programming appraoch, and we will write our own function. In R, we use the function called 'function' to create a function. R functions return a single object

```{r purrr}
dept_abbrv = c('acc', 'bus', 'isa', 'mkt')

# TS function takes an abbrv as an input and returned a data_frame as an output
scrape_my_bulletin = function(abbrv){
  bulletin_url = paste0('https://bulletin.miamioh.edu/courses-instruction/', abbrv, '/')
# Made the webpage an R object because we're gonna be using it several times while only changng the URL
webpage = rvest::read_html(bulletin_url)

webpage |> rvest::html_elements("p.courseblocktitle") |> rvest::html_text2() -> titles
webpage |> rvest::html_elements("p.courseblockdesc") |> rvest::html_text2() -> descs

df = data.frame(title = titles, desc = descs)
return(df)
}

test = scrape_my_bulletin(abbrv = 'eco')

# To use function from purrr, we will use a map_*() or a map2_*() or a pmap_*()
# map uses a function that takes a single input (or you're changing a single input)
# map2 uses a function that takes 2 inputs
# pmap >= 3
# after the _, you put the type of object you are getting back

# The .x is the vector that we will iterate over and the .f is the function we use
courses_df_from_purr = purrr::map_df(.x = dept_abbrv, .f = scrape_my_bulletin )

```


## Scrape data from the website <https://www.planecrashinfo.com/> and it has a database of plane crashed by year

```{r}
year = 2025
crash_url = paste0('https://www.planecrashinfo.com/', year, '/', year, '.htm')
crash_page = rvest::read_html(crash_url)
```

